---
title: "Using labellr"
author: "Oisin Fitzgerald"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

*Incomplete*

```{r, include=FALSE}
## get locations of files
package_loc <- system.file(package = "labellr")
ext_path <- file.path(package_loc, "extdata")
```

The motivation behind `labellr` is the following. You need to categorise each row of a data frame into 
one of (many) possible levels of a summary variable. This categorisation can be done according to a set
of rules that is defined in advance. However, writing code that performs this categorisation would
be lengthy, making it difficult to debug and understand for newbies. For example, you may have a medical
dataset that contains detailed descriptions of measurements, diagnosis codes and outcomes but that 
needs the addition of one or more summary variables to be useful for anlaysis.
The goal of `labellr` is to minimise the number of lines of code required in categorising the data by allowing the use of tabular files (e.g. MS Excel, Google ??) to define each level of the summary variable. It does this by.. 
As a toy example, suppose a medical clinic performs either X-ray, FMRI or some form of surgery. Using 
your preferred tabular data editor you define the levels of the summary variable treatment. Entering
a 1 indicates this value must be present, while entering a 0 indicates this value must be absent. Leaving a cell blank (assuming blank in read into R as NA) will allow that variable to take any value. 

```{r}
tmt_def <- read.csv(file.path(ext_path, "treatment_definitions.csv"))
tmt_def
```
